Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-30 manuscript/manuscript.tex
unceratinty test notes added

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Time series of average percent cover of our four focal species:
\emph{Bouteloua gracilis} (BOGR), \emph{Hesperostipa comata} (HECO),
\emph{Pascopyrum smithii} (PASM), and \emph{Poa secunda} (POSE).}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Time series of average percent cover over all quadrats for our
four focal species: \emph{Bouteloua gracilis} (BOGR), \emph{Hesperostipa
comata} (HECO), \emph{Pascopyrum smithii} (PASM), and \emph{Poa secunda}
(POSE). Light grey lines show trajectories of individual quadrats. Note
the different y-axis scales across panels.}
\end{figure}
